test plot resize

### 2018-05-11 inst/documents/rotations_notes.Rmd
pap3

in insecticide_check()
BE CAREFUL!

df_ins <- data.frame(last_used=rep(NA, n_insecticides))

@@

>>>>

in insecticide_switch()
BE CAREFUL!

min_gens_switch_back minimum num gens before can switch back to an insecticide

I set the default in run_rot to 10 generations.
(I can leave min_rwr_interval in for now, when it is set to 1 it has no effect).

Note that min_rwr_interval was assessed in insecticide_check() i.e. it stopped an insecticide from being stopped within a certain interval

Which actually maybe wasn't so bad ?? Maybe I could stick with it ??
i.e. that simulated not being able to withdraw an insecticide which has already been applied (which sounds pretty good now I think about it ...)

Either of these could be OK. I had it set to 5 generations before which was half a year.

@@

Decide whether to use min_rwr_interval OR min_gens_switch_back
